A Technique for Inter-Retailer Recommendations

### 2014-06-11 paper2/paper.tex
Add first draft abstract.

\section*{Abstract}
\emph{Abstracts are abstract. They confront you. There was a reviewer a
while back who wrote that my papers didn't have any beginning or any end. He
didn't mean it as a compliment, but it was.} --Jackson Pollock

@@

\subsection*{\em LatentFeatureRecommender}
Although the $NeighborhoodRecommender$ leverages the information contained in
the recommendation graphs to some extent, it is still primarily based on product
descriptions. Presumably, the graphs are derivative of a collaborative filtering
scheme, and hence, reveal associations between products that are not evident
from the language of their descriptions. For example, a dress's description
might not capture if it is more conservative or more risque. Yet, this could be
the salient feature it has in common with an associated recommendation.  These
sort of abstract, perhaps ineffable, features can be essential to item-item
relations. We must therefore ask whether we can more fully utilize the given
graphical information to discover these latent features in order to choose
better inter-catalogue recommendations.

>>>>

\section*{Abstract}
\emph{The problem of making recommendation across retailers using only publicly
available information is explored. Experiments are conducted using real data in
which several recommender algorithms are compared. A novel latent feature
inter-retailer recommender algorithm that leverages public intra-retailer
recommendation information is described and shown to outperform a nontrivial
content-based approach.}

@@

\subsection*{\em LatentFeatureRecommender}
Although the $NeighborhoodRecommender$ leverages the information contained in
the recommendation graphs to some extent, it is still primarily based on product
descriptions. Presumably, the graphs are derivative of a collaborative filtering
scheme, and hence, reveal associations between products that are not evident
from the language of their descriptions. For example, a dress's description
might not capture whether it is more conservative or more risque. Yet, this
could be the salient feature it has in common with an associated recommendation.
These sort of abstract, perhaps ineffable, features can be essential to
item-item relations. We must therefore ask whether we can more fully utilize the
given graphical information to discover these latent features in order to choose
better inter-catalogue recommendations.
